# (PART) Demonstration {-}

# Options for running demos
Underlying files & source code can be accessed via [GitHub repository](https://github.com/utah-dwq/irTools-test-16){target="_blank"}.  
Demo tools can be accessed and run in three ways:

## Preferred method: R-Studio Cloud
A cloud workspace and R-project with DWQ's R packages and dependencies pre-installed can be accessed through R-Studio Cloud.  
First, [sign up for an R-Studio account](https://login.rstudio.cloud/register?redirect=https%3A%2F%2Fclient.login.rstudio.cloud%2Foauth%2Flogin%3Fshow_auth%3D0%26show_login%3D1%26show_setup%3D1){target="_blank"} if you don't already have one. 
Accounts are free, and logins via existing Google or GitHub accounts are OK.  
Then, access the project for this demonstration at [rstudio.cloud/project/360104](https://rstudio.cloud/project/360104){target="_blank"}. Opening this link will generate a temorary copy of the demonstration 
project on your account. There you are able to import DWQ R package libraries and run functions and applications.  
For example, 
```{r, eval=F}
library(irTools)
asmntDashboard()
```

## Local install of R & DWQ packages
Install R [r-project.org](https://www.r-project.org/){target="_blank"} and/or R-Studio [rstudio.com/products/rstudio/download/](https://www.rstudio.com/products/rstudio/download/){target="_blank"} if not already installed on your computer.    
Installing DWQ's R packages from GitHub to your local R installation requires the package, 'devtools'.  
To install devtools & DWQ's R packages:
```{r, eval=F}
install.packages('devtools')
devtools::install_github('utah-dwq/irTools')
library(irTools)
asmntDashboard()
```

If you encounter issues installing one or more package dependencies, e.g.:  
```{r, eval=F}
Error in loadNamespace(j <- i[[1L]], c(lib.loc, .libPaths()), versionCheck = vI[[j]]) :  
there is no package called ‘glue’
```

Attempt a manual install of that package and re-try.
```{r, eval=F}
install.packages('glue')
devtools::install_github('utah-dwq/irTools')
```

## Running Shiny applications via remote server
Most applications included in this demo have also been deployed to a remote server where they can be accessed via a web browser without installing R, packages, or creating a login. See the 'Applications' section of this document for more information. 
Note that applications running on the remote server may run a bit slower and time-out after 15 minutes of inactivity.

# Packages & data downloads
## Install & import DWQ's R packages
```{r, packages, eval=F}
devtools::install_github('utah-dwq/wqTools')
devtools::install_github('utah-dwq/irTools')
```

```{r, libraries}
library(wqTools)
library(irTools)
```

## Download and import data
### Data download
```{r, download1, eval=F}
downloadWQP(outfile_path='01-raw-data',start_date='10/01/2008', end_date='09/30/2014', zip=TRUE, unzip=TRUE, retrieve=c("narrowresult", "activity", "detquantlim"))
downloadWQP(outfile_path='01-raw-data', zip=FALSE, retrieve="sites")
```
*Note--* Downloading all sites separately (query w/o date range), then subsetting to just those included in narrowresult.

```{r, download2, eval=F}
sites=read.csv(file='01-raw-data/sites-2019-04-04.csv')
nr=read.csv(file='01-raw-data/narrowresult-2019-04-04.csv')
sites=sites[sites$MonitoringLocationIdentifier %in% nr$MonitoringLocationIdentifier,]
write.csv(file='01-raw-data/sites-2019-04-04.csv', sites, row.names=F)
rm(sites)
```


### Data imports
Read raw data into R, remove duplicates and check for orphans
```{r, data-import, cache=T}
irdata <- readWQPFiles(file_select=FALSE,
            narrowresult_file = "01-raw-data\\narrowresult-2019-04-04.csv",
            sites_file = "01-raw-data\\sites-2019-04-04.csv",
            activity_file = "01-raw-data\\activity-2019-04-04.csv",
            detquantlim_file = "01-raw-data\\detquantlim-2019-04-04.csv",
            orph_check = TRUE)

objects(irdata)
```


