# (PART) Demonstration {-}

# Packages & data downloads
## Install & import DWQ's R packages
```{r, packages, eval=F}
devtools::install_github('utah-dwq/wqTools')
devtools::install_github('utah-dwq/irTools')
```

```{r, libraries}
library(wqTools)
library(irTools)
```

## Download and import data
### Data download
```{r, download1, eval=F}
downloadWQP(outfile_path='01-raw-data',start_date='10/01/2008', end_date='09/30/2014', zip=TRUE, unzip=TRUE, retrieve=c("narrowresult", "activity", "detquantlim"))
downloadWQP(outfile_path='01-raw-data', zip=FALSE, retrieve="sites")
```
*Note--* Having an issue downloading sites for POR date range (Unclear why exactly. Seems to be associated applying date query parameters to older sites). Downloading all sites separately, then subsetting to just those included in narrowresult.

```{r, download2, eval=F}
sites=read.csv(file='01-raw-data/sites-2019-04-04.csv')
nr=read.csv(file='01-raw-data/narrowresult-2019-04-04.csv')
sites=sites[sites$MonitoringLocationIdentifier %in% nr$MonitoringLocationIdentifier,]
write.csv(file='01-raw-data/sites-2019-04-04.csv', sites, row.names=F)
rm(sites)
```


### Data imports
Read raw data into R, remove duplicates and check for orphans
```{r, data-import, cache=T}
irdata <- readWQPFiles(file_select=FALSE,
            narrowresult_file = "01-raw-data\\narrowresult-2019-04-04.csv",
            sites_file = "01-raw-data\\sites-2019-04-04.csv",
            activity_file = "01-raw-data\\activity-2019-04-04.csv",
            detquantlim_file = "01-raw-data\\detquantlim-2019-04-04.csv",
            orph_check = TRUE)

objects(irdata)
```


