
# Site validation


## Auto site validation
```{r, site-auto-validate, eval=F}
autoValidateWQPsites(
	sites_object=irdata$sites,
	master_site_file="02-site-validation/IR_master_site_file.csv",
	waterbody_type_file = "lookup-tables/waterbody_type_domain_table.csv",
	polygon_path="02-site-validation/polygons",
	outfile_path="02-site-validation"
	)
```

## Manual site validation
Performed a test manual site validation by accepting, rejecting, and merging a number of sites through multiple iterations of the application. See '02-site-validation' folder. 
Data from all sites still requiring review will be rejected at a later step. A 'ReviewComment' column was manually added to the master site list file. The site list and flat reasons files were 
manually added to a single .xlsx workbook to interface with the site review application (tabnames 'sites' and 'reasons').

[Site review application](https://udwq.shinyapps.io/site-review-demo/)

```{r, site-man-validate, eval=F}
runSiteValApp()
```



