
# Data processing

## Data validation
Table-based validation.  
Functions to update & apply data validation tables, generate data with consistent nomenclature.  
1. Labs & activity types  
2. Activity media  
3. Parameter names & fractions  
4. Detection conditions  
5. Detection limit types  
6. Unit conversion factors  
7. Apply screening tables and subset to accepted data  
<br><br>

```{r, id-transwb, echo=FALSE}
translation_wb="00-lookup-tables\\ir_translation_workbook.xlsx"
```

### Update detection condition / limit name tables
```{r, update-detcondlim}
updateDetCondLimTables(results=irdata$merged_results, detquantlim=irdata$detquantlim, translation_wb=translation_wb,
						detConditionTable_startRow=2, detLimitTypeTable_startRow=2)
```


### Determine detection conditions and fill NDs
```{r, fill-masked}
merged_results_filled=fillMaskedValues(results=irdata$merged_results, detquantlim=irdata$detquantlim, translation_wb=translation_wb,
									   detLimitTypeTable_sheetname="detLimitTypeTable", detLimitTypeTable_startRow=2,
									   unitConvTable_sheetname="unitConvTable", unitConvTable_startRow=1, unitConvTable_startCol=1,
									   lql_fac=0.5, uql_fac=1)
```

### Update lab/activity & media tables
```{r, labactmedia}
updateLabActMediaTables(merged_results_filled, translation_wb=translation_wb, labNameActivityTable_startRow = 2)
```


### Apply screening tables
```{r, screening-tables}
mrf_screened=applyScreenTable(merged_results_filled,wb=translation_wb,
								sheetname="sites",startRow=2, flag_col_name="IR_Site_FLAG", com_col_name="IR_Site_COMMENT")

mrf_screened=applyScreenTable(mrf_screened,wb=translation_wb,
								sheetname="detConditionTable",startRow=2, flag_col_name="IR_DetCond_FLAG", com_col_name="IR_DetCond_COMMENT")

mrf_screened=applyScreenTable(mrf_screened,wb=translation_wb,
								sheetname="labNameActivityTable",startRow=2,flag_col_name="IR_LabAct_FLAG", com_col_name="IR_LabAct_COMMENT")

mrf_screened=applyScreenTable(mrf_screened,wb=translation_wb,
								sheetname="activityMediaNameTable",startRow=1, flag_col_name="IR_Media_FLAG", com_col_name="IR_Media_COMMENT")

```


### Subset data to desired flag types
```{r, screen-subset}
mrf_sub=subset(mrf_screened,
	IR_DetCond_FLAG=="ACCEPT" &
	IR_LabAct_FLAG=="ACCEPT" &
	IR_Media_FLAG=="ACCEPT" &
	IR_Site_FLAG =="ACCEPT")
```

## Data prep
Generating assessable dataset  

1. Assigning criteria (by parameter & use via criteria table)  
2. Convert to consistent units (target units defined by criteria)  
3. Check that data fractions & activities match assessment targets  
4. Aggregate to daily values  
5. Generate correction factors & calculate criteria  
6. Split data into assessment groups  
<br><br>


### Update parameter translation tables
```{r, update-param-trans, eval=F}
updateParamTrans(data=mrf_sub, detquantlim=detquantlim,  translation_wb="00-lookup-tables\\ir_translation_workbook_live.xlsx")
```

### Apply parameter translation table
```{r, apply-param-trans}
mrf_sub_translated=applyScreenTable(mrf_sub,wb=translation_wb,
									sheetname="paramTransTable",startRow=4,flag_col_name="IR_Parameter_FLAG",com_col_name="IR_Parameter_COMMENT",
									na_dup_err=F)
```
### Subset data to ACCEPT parameters
```{r, sub-accept-params}
accept_data=subset(mrf_sub_translated, IR_Parameter_FLAG=="ACCEPT")
```

```{r, echo=F}
tab=data.frame(table(droplevels(accept_data$CharacteristicName)))
names(tab)=c('Parameter', 'Count')
```
```{r, echo=F}
knitr::kable(tab, caption='Accepted parameter sample counts.')
```


### Criteria & unit assigments

#### Assign criteria
```{r, assign-criteria}
data_crit=assignCriteria(accept_data, crit_wb="00-lookup-tables\\IR_uses_standards.xlsx",
								  crit_sheetname="criteria", ss_sheetname="ss_criteria", crit_startRow=1, ss_startRow=1, rm_nocrit=FALSE, print=FALSE)
```
<br><br>

```{r, echo=F}
tab=unique(data.frame(data_crit[,c('IR_MLID', 'IR_MLNAME','ASSESS_ID','Water_Type','ActivityStartDate','R3172ParameterName','IR_Value','IR_Unit','IR_DetCond','BeneficialUse','CriterionLabel', 'NumericCriterion','CriterionUnits', 'AsmntAggFun', 'SSC_StartMon','SSC_EndMon','SSC_MLID')]))
sites_all=unique(data_crit$IR_MLID)
sites_sel=sample(sites_all,10)
sites_sel=unique(append(sites_sel,'UTAHDWQ_WQX-4960740'))
tab=subset(tab, IR_MLID %in% sites_sel)
tab=subset(tab, !is.na(NumericCriterion))
tab=data.frame(lapply(tab, as.factor))
```

<br>
```{r, echo=F, fig.cap='Example data with criteria assigned. Note the site specific standard assignment example of Blue Creek (MLID UTAHDWQ_WQX-4960740).'}
DT::datatable(tab, rownames=FALSE, filter="top",
				options = list(scrollY = '600px', scrollX=TRUE, paging = TRUE, dom="tpr", deferRender = TRUE)
			)
```

<br><br>




#### Update unit conversion table
```{r, update-unit-conv}
updateUnitConvTable(data_crit, translation_wb, sheetname = "unitConvTable")
```
<br><br>

### Final data prep step
```{r, data-prep}
prepped_data=dataPrep(data=data_crit, translation_wb=translation_wb, split_agg_tds=TRUE, crit_wb="00-lookup-tables\\IR_uses_standards.xlsx",
						unit_sheetname = "unitConvTable", startRow_unit = 1, cf_formulas_sheetname="cf_formulas", startRow_formulas=1)
attach(prepped_data)
```

```{r, echo=F}
tab=unique(data.frame(toxics[,c('IR_MLID', 'IR_MLNAME','ASSESS_ID','ActivityStartDate','R3172ParameterName','IR_Value','IR_Unit','BeneficialUse','CriterionLabel', 'NumericCriterion','CriterionUnits', 
	'CalculatedCrit','hardness','cf_max_pH_pH units','cf_max_Temperature, water_deg C','cf_min_Calcium_mg/l','cf_min_Magnesium_mg/l','cf_min_pH_pH units','CF', 'CriterionFormula')]))
tab=subset(tab, IR_MLID %in% sites_sel)
tab=subset(tab, !is.na(NumericCriterion))
tab=data.frame(lapply(tab, as.factor))
```

<br>
```{r, echo=F, fig.cap='Example final prepped data (toxics). Note that units have been converted match criteria, hardness has been calculated, and correction factors have been applied to calculate formula-based criteria.'}
DT::datatable(tab, rownames=FALSE, filter="top",
				options = list(scrollY = '600px', scrollX=TRUE, paging = TRUE, dom="tpr", deferRender = TRUE)
			)
```










